---
title: "Getting Started with Partial Clique Simulation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with Partial Clique Simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Partial Clique Simulation and Analysis

Welcome! This vignette demonstrates how to use the core functions of the `UWBiost561` package for generating, analyzing, and benchmarking graphs with planted partial cliques.

---

## 1. Generating a Partial Clique Graph

Let's start by generating a random adjacency matrix with a planted partial clique using `generate_partial_clique()`:

```{r, message=FALSE}
library(UWBiost561)

set.seed(123)
sim <- generate_partial_clique(
  n = 10,
  clique_fraction = 0.5,
  clique_edge_density = 0.8
)
adj_mat <- sim$adj_mat

# Print adjacency matrix
adj_mat

```
We have now generated a 10x10 adjacency matrix. Each entry indicates whether an edge exists between two nodes. The partial clique is "planted" according to the specified parameters.

2. Finding a Maximal Partial Clique
Next, we use compute_maximal_partial_clique7() to find a maximal partial clique with a desired edge density threshold (alpha). Here, we use alpha = 0.7:

```{r}

result <- compute_maximal_partial_clique7(
  adj_mat = adj_mat,
  alpha = 0.7
)

cat("Nodes in maximal partial clique:", result$clique_idx, "\n")
cat("Edge density in clique:", result$edge_density, "\n")

```


3. Running a Simulation Study
Finally, let's run a small simulation study to compare performance across different settings.
We simulate graphs of size 10 and 20, test two different density thresholds (alpha), and repeat each setting twice:
```{r}
sim_results <- simulate_partial_clique_study(
  n_values = c(10, 20),
  alpha_values = c(0.7, 0.9),
  n_trials = 2,
  time_limit = 3
)

head(sim_results)

```
You can further summarize or visualize the results with your favorite tools (e.g., dplyr, ggplot2).
For example, let's summarize average clique size by n and alpha:
```{r}

library(dplyr)
summary_stats <- sim_results %>%
  group_by(n, alpha) %>%
  summarize(
    avg_clique_size = mean(clique_size, na.rm = TRUE),
    error_rate = mean(error, na.rm = TRUE)
  )

summary_stats
